DRAFT: Scalable, Robust Multipath Communication on the Butterfly Network

### 2018-05-22 plosone/attack.tex
More revisions based on www feedback.

It is important to note that the butterfly is a highly structured and constrained
network topology,
very different form those found in social networks and other
self-organized networks.
The reader may wonder whether it is realistic or useful to assume such control over
the network structure.
We have already seen that whenever a single point of failure exists in the network,
there is a potential for an attacker to exploit it through coercion.
So we claim that {\em attack-tolerance cannot be achieved without the ability to influence
network structure}.
Luckily, there are scenarios in which network topology can be dictated.
Examples include overlay networks
\cite{lua_survey_2005, korzun_structured_2013},
formal organizations \cite{mohr_explaining_1982},
government-regulated cellular networks \cite{walker_mass_2012},
and call tree notification systems \cite{nickerson_thinking_2010}.
In general,
{\em when the need for attack-tolerance is high enough to warrant investment
in infrastructure, networks can be engineered and maintained as infrastructure}.
It is also worth noting that attack-tolerant networks may be sub-components of
larger, less-constrained systems.
For example, a single server might be replaced by a distributed network of servers,
each with different ownership, physical location, and legal jurisdiction,
without placing any unrealistic constraints on the clients connecting to
those servers.

Our main contributions are:
\begin{itemize}
\item{
We propose a novel structured multipath fault tolerance (SMFT) scheme
for extending standard fault tolerance techniques to
{\em adversarial} faults in {\em complex networks}.
We do so by showing that the probability of detecting adversarial faults
approaches 1 exponentially with the number of {\em independent paths},
and that with $h$-degree {\em bounded trust transitivity},
all $h$-internally vertex disjoint paths are independent.
}
\item{We prove that the number of $h$-internally vertex disjoint
paths between two nodes in a wrap-around butterfly network
is at least $2^h$,
and present a scalable and efficient concurrent multipath routing (CMR) algorithm
to find these paths,
which can be combined with SMFT to achieve a high level of attack-tolerance.
}
\item{We show that rewiring a snapshot of the internet's router network with
edges from a butterfly network allows it to tolerate a higher number of failures
without fragmenting, and increases the effective redundancy in the presence
of a large number of adversarial faults.}
\end{itemize}

@@

There has been considerable work on trust-based attack-tolerance techniques
in network security, both centralized and decentralized.
Centralized approaches such as {\em public key infrastructure} (PKI)
suffer from a number of vulnerabilities
\cite{ellison_ten_2000}, including vulnerability to coercion,
which stems largely from the single points of failure inherent to
centralization.
The well-known and widely-used {\em web of trust} approach
\cite{zimmermann_official_1995,richters_trust_2011}
is a decentralized alternative.
In a web of trust,
individuals choose who they trust initially.
Trust is then extended to new individuals if they are vouched for by a
currently-trusted individual.
Infinite trust transitivity is helpful for establishing a large group of
trusted nodes, but unfortunately unrealistic
\cite{christianson_why_1997}.
Additionally, the web of trust approach
does not distinguish between paths of different lengths.
Our work addresses both of these limitations by requiring only
bounded trust transitivity.

@@

Fig. \ref{fig:pfail} shows the value of $p_f$
as a function of $k$ and $l$.
Eq. (\ref{eq:pf_approx}) shows that while $p_f$
depends on the fractions of
channels actually utilized $\alpha$ and compromised $\beta$,
it decreases exponentially with $\delta$.
This result is significant because,
as we will soon show, $\delta$
depends only on the network structure
and the strength of trust transitivity.
{\em Thus, the scheme can be effective, even when the number of channels used
$k$ is a small fraction of the channels available}.
In other words, this scheme exhibits a {\em stabilizing asymmetry:}
senders can tolerate attacks from significantly more powerful
adversaries,
as long as the network provides large $\delta$.

\begin{figure}[!h]
\centerline{\includegraphics{fig-perror}}
\caption{
The probability of an undetectable error as a function of the number of
redundant channels and the number of adversarial faults.
}
\label{fig:pfail}
\end{figure}

>>>>

It is important to note that the butterfly is a highly structured and constrained
network topology,
very different form those found in social networks and other
self-organized networks.
The reader may wonder whether it is realistic or useful to assume such control over
the network structure.
Regardless of implementation difficulty,
we argue that {\em attack-tolerance cannot be achieved without the ability to influence
network structure}.
Targeted attacks, by definition, target single points of failure.
Attack tolerance can thus be achieved in two ways: 1. preventing failure at
those points, or 2. preventing the existence of central points.
Because individual points are always vulnerable to coercive, non-technological
attacks, the former method is insufficient.
We must instead rely on some control over topology to prevent the existence of
single points of failure.
The difficulty of achieving control over network topology can be mitigated by
a number of approaches.
Attack-tolerant networks might be sub-components of
larger, less-constrained systems.
For example, a single centralized server might be replaced by a distributed
network of servers,
each with different ownership, physical location, and legal jurisdiction,
without placing any unrealistic constraints on the clients connecting to
those servers.
When attack tolerant topologies are nested (as in the case of the butterfly
topology), multiple independent sub-components could be merged into larger
ones over time.
Real-world examples of structured neworks include: overlay networks
\cite{lua_survey_2005, korzun_structured_2013},
formal organizations \cite{mohr_explaining_1982},
government-regulated cellular networks \cite{walker_mass_2012},
and call tree notification systems \cite{nickerson_thinking_2010}.
In general,
{\em when the need for attack-tolerance is high enough to warrant investment
in infrastructure, topology can be engineered and maintained as infrastructure}.

Our main contributions are:
\begin{itemize}
\item{
We propose a novel structured multipath fault tolerance (SMFT) scheme
for extending standard fault tolerance techniques to
{\em adversarial} faults in {\em complex networks}.
Assuming $h$-degree {\em bounded trust transitivity},
We show that the probability of detecting adversarial faults
$h$-internally vertex disjoint paths.
}
\item{We prove that the number of $h$-internally vertex disjoint
paths between two nodes in a wrap-around butterfly network
is at least $2^h$,
and present a scalable and efficient concurrent multipath routing (CMR) algorithm
to find these paths,
which can be combined with SMFT to achieve a high level of attack-tolerance.
}
\item{We show that rewiring a the edges of the internet's router network to
resemble a butterfly network allows it to tolerate a higher number of failures
without fragmenting, and increases the effective redundancy in the presence
of a large number of adversarial faults.}
\end{itemize}

@@

There has been considerable work on trust-based attack-tolerance techniques
in network security, both centralized and decentralized.
Centralized approaches such as {\em public key infrastructure} (PKI)
suffer from a number of vulnerabilities
\cite{ellison_ten_2000}, including vulnerability to coercion,
which stems largely from the single points of failure inherent to
centralization.
The well-known and widely-used {\em web of trust} approach
\cite{zimmermann_official_1995,richters_trust_2011}
is a decentralized alternative.
In a web of trust,
individuals can have {\em direct trust},
as well as {\em indirect trust} for those trusted by someone directly trusted.
Typically, this transitivity is extended to any number of hops,
sometimes reducing trust by a multiplicative factor at each hop.
Infinite trust transitivity is helpful for establishing a large group of
trusted nodes, but unfortunately unrealistic
\cite{christianson_why_1997}.
Our work addresses this limitation by assuming only
bounded trust transitivity.

@@

Fig. \ref{fig:pfail} shows the value of $p_f$
as a function of $k$ and $l$.
Eq. (\ref{eq:pf_approx}) shows that while $p_f$
depends on the fractions of
channels actually utilized $\alpha$ and compromised $\beta$,
it decreases exponentially with $\delta$.
This result is significant because,
as we will soon show, $\delta$
depends only on the network structure
and the strength of trust transitivity.
{\em Thus, the scheme can be effective, even when the number of channels used
$k$ is a small fraction of the channels available}.
In other words, this scheme exhibits a {\em stabilizing asymmetry:}
senders can tolerate attacks from significantly more powerful
adversaries.
Furthermore, this scheme requires only a small increase in network traffic
as long as the network provides a large number of independent paths $\delta$.

\begin{figure}[!h]
\centerline{\includegraphics{fig-perror}}
\caption{
The probability of an undetectable error as a function of the number of
redundant channels and the number of adversarial faults.
A small increase in the number of utilized paths (network traffic)
can compensate for a large increase in attacker power.
}
\label{fig:pfail}
\end{figure}
